Trademap_Data_Analysis

### 2018-12-16 sourceCode/Analysis_Data_Muh.Rmd

import_Product_Group <- import_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)

@@

The effects of countries may be change year by year. So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
It is clear that China,Germany and Russia are more effect than others.
```{r }
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  #filter (year == 2017)%>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

@@

```{r}
Import_Value_by_product <- import_Product_Group %>%
  filter (Country %in% c("China","Germany","Russian"))%>%
  group_by(Country,Product_Group_Code,Product_Group_Name)%>%
  summarize (Average_Import_Value = mean(Import_Value))

@@

Import_Value_by_product<- Import_Value_by_product %>%
  group_by(Country) %>% 
  mutate(Cum_Import_Pct = cumsum(Average_Import_pct)) %>%
  filter (Cum_Import_Pct <= 70)

>>>>

import_Product_Group <- import_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Value =Values)

@@

The effects of countries may be change year by year. So that as an alternative perspective we could average net value for all countries in five years and normalized that value to show which country's effects are more than others.
It is clear that China,Germany and Russia are more effect than others.
```{r }
#Normalized of Average Values for five years
Normalized_Values_By_Country <- Export_Import_JTable %>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

@@

```{r}
Normalized_Values_By_Country <- Export_Import_JTable %>%
  group_by(Country)%>%
  summarize (Net_Value = mean(Export_Value - Import_Value))%>%
  mutate(normalized_Net_value =  round((Net_Value  - mean(Net_Value))/sd(Net_Value ),2)) %>%
  mutate(value_Net_type =  ifelse(normalized_Net_value < 0, "below", "above"))

Country_type <- Normalized_Values_By_Country%>%
   select( Country, value_Net_type)

import_Product_Group  <- import_Product_Group %>%
left_join(Country_type,value_Net_type,by = "Country")

Import_Value_by_product <- import_Product_Group %>%
  filter (value_Net_type == "below" )%>%
  group_by(Country,Product_Group_Code,Product_Group_Name)%>%
  summarize (Average_Import_Value = mean(Import_Value))

@@

Import_Value_by_product<- Import_Value_by_product %>%
  group_by(Country) %>% 
  mutate(Cum_Import_Pct = cumsum(Average_Import_pct))
